%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Novjean J Kannathara} % Your name
\address{8335 Freedom Crossing Trl, Jacksonville, Florida 32256}
%\address{280 Chiquita Avenue \\ Mountain View, California - 94041, USA}
%\address{3685 De Soto Dr, West Lafayette, Indiana 47906}
%\address{909 112th Avenue NE \\ Bellevue, Washington 98004} % Your address
%\address{3218 Pine Valley Way, Piscataway, New Jersey 08854} % Your address
%\address{201 North Squirrel Road, Auburn Hills, MI 48326}
%\address{6762 Warner Avenue \\ Huntington Beach, California 92467} % Your secondary address (optional)
\address{(765)~$\cdot$~476~$\cdot$~3695 \\ novjeanj@gmail.com} % Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%    EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Purdue University, West Lafayette} \hfill {\em May 2016} \\ 
M.S. in Computer and Information Technology \\
Minor in Data Analytics\\
Student at Nvidia Research Lab, Purdue University \smallskip \\
Overall GPA: 3.74

\end{rSection}

%----------------------------------------------------------------------------------------
%    TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technology & Java, C#, Servlets, Spring, RESTful, Hadoop, \\
&   Struts, JUnit, Selenium, XML, HTML, C \\
App Development & Xamarin.Forms, React-Native, Redux, Android, iOS \\
UI & HTML, CSS3, AngularJS, Bootstrap, Express, JavaScript \\
Databases \& tools & MySQL, Hibernate, MongoDB, PostgreSQL, HiveQL, JSON, Postman\\
Application Servers & Tomcat, Node.js\\
Cloud Services & AWS, Docker \\
IDE & Eclipse, Visual Studio, Atom, Android Studio, SublimeText, IntelliJ, Netbeans
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%    WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------

\begin{rSubsection}{Core Computing Solution}{August 2017 - Present}{Software Engineer}{Jacksonville, FL}
\item Responsible for development of cross-platform iOS/Android application using Xamarin Forms.
\item Utilizing remote notifications through Firebase for triggering activities on both iOS/Android version.
\item Implementing AWS SDK within Xamarin to utilize AWS tools S3 and SNS.
\item Developing an Android component for RFID tag detection utilizing ThingMagic M6e and Raspberry Pi.
\item Conduct interviews for potential software developers from the University of North Florida..
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Virtual Doorman}{April 2017 - August 2017}{Mobile Application Developer}{Jacksonville, FL}
\item Developed iOS/Android app for resident portal using React-Native and Xamarin Forms.
\item Created App pages using React Native, Redux utilizing React-native-router-flux, Babel and Watchman.
\item Designed and developed updated database models with offshore team in Pakistan for fully REST implementation. 
\item Responsible for marketing of the Virtual Doorman service through Facebook, LinkedIn and remodeling corporate Page to improve and increase customer experience.
%\item App creation design and development in Android Studio based on MEAN stack SPA. 
% \item SQL (MySQL, TSQL) and NoSQL (MongoDB) research in database connectivity using JavaScript.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Patton Labs}{January 2017 - April 2017}{Full Stack Java Developer}{Jacksonville, FL}
\item Realized Hibernate ORM with Spring backend conversion of Ayuber inventory management portal.
\item Designed schema diagram in Salesforce Force application for customer management from the present data model. Created Joined and Summary performance reports and also developed app dashboard.
\item Developed single page application for training portal using AngularJS 1.6, Express, Node.js, and MongoDB.
%\item App creation design and development in Android Studio based on MEAN stack SPA. 
\item SQL (MySQL, TSQL) and NoSQL (MongoDB) research in database connectivity using JavaScript.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{SocioTronics LLC}{August 2016 - December 2016}{Technical Intern}{Orlando, FL}
\item Developed chaining of MapReduce operations using Python on Canopy using MRJob and MRStep.
\item Deployed and monitored MapReduce in Java through Cloudera using Hue and Hive.
\item Manipulated data to obtain business intelligence utilizing MapReduce and R.
\item Tableau visualization representation of results obtain from Hive querying.
%\item Mastered OOP's concept using Scala as the language during my tenure here.
\end{rSubsection}

%----------------------------------------------

\begin{rSubsection}{Purdue University}{August 2014 - May 2016}{Graduate Teaching Assistant - C Programming}{West Lafayette, IN}
\item Administer lab sessions multiple days in a week for C Programming concepts offered by Guity Ravai.
\item Implemented several interactive teaching methods such as Impact classrooms, excessive code commenting and E-interactive programming book with varying results in student grade performances.
\item Designed and educated homeworks and exams throughout the tenure for more than 300 students.
%\item Performed teaching-related duties such as grade book management, examination auditing and weekend special classes to assist faculty members and students.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Purdue University}{January 2016 - May 2016}{Graduate Teaching Assistant- Software Development Concepts}{West Lafayette, IN}
\item Responsible for the pedagogy and supervision of lab sessions for C\# programming for 60 students.
\item Maintained assessments, scheming scoring rubrics, and grade information storage.
\item Designed assignments and exams with teaching related duties to assist faculty members and educators.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Independent Contractor}{July 2011 - February 2013}{Web Application Developer}{Kochi, India}
\item Web Based clients domains included retail, portfolio, and entertainment utilizing SEO tools.
\item Matured backend development skills implementing JSP, HTML using Java, JDBC and MySQL.
%\item Managed two developers and two designers throughout the tenure for several time-constrained projects.
%\item Marketed services to more than  500 companies in Kochi and Thiruvananthapuram regions of Kerala.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%    TECHNICAL PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Indoor Navigation Aid System for Visually Impaired People}{January 2016 - May 2016}{}{}
\item Develop an Arduino Lilypad based handheld device to aid blind/visually impaired people to navigate unknown environments independently and effectively considering cost-effectiveness simultaneously.
\item Objective was to eliminate the need of mobility training through Orientation and Mobility instructors.
%\item Created the prototype and is in continued research successfully passing IRB approval.
\end{rSubsection}

\begin{rSubsection}{Yelp Academic Data Challenge}{August 2013 - December 2015}{}{}
\item Objective is to obtain a direct correlation between Yelp business user's review words to star ratings.
\item Determined relations between service/amenities to star rating utilizing Hadoop and HiveQL.
\item Visualization of results represented graphically through Tableau.
\end{rSubsection}

\begin{rSubsection}{Multi-cluster Deployment of Data Stores using LXC's}{August 2014 - August 2015}{}{}
\item Deployment of clusters of Linux containers running Redis database on a national scale.
\item Objective was to confirm the stability of Redis"s replication property over LXC clusters.
\item Funded by Amazon as the cluster spawning was achieved using AWS such as EC2 and EMR.
\item Obtained stable cluster system capable of handling data transmission over multiple nodes and clusters.
\end{rSubsection}

\begin{rSubsection}{Docker EC2 Deployment implementing Hadoop}{May 2014 - August 2014}{}{}
\item Researched Docker container integration through AWS tools including EC2, EMR, and S3. 
\item Deployed command line interface scripts to automate the deployment of multiple Linux Docker containers.
\end{rSubsection}

\begin{rSubsection}{IMDB Database Intelligence / Analytics}{January 2014 - May 2014}{}{}
\item Performed MapReduce operations on IMDB database using Hadoop, EC2, EMR and HiveQL.
\item Calculated efficiency in the cluster configuration to run Hadoop analysis over different EC2 machines.
\item Spawned several EC2 cluster configurations through AWS CLI.
\end{rSubsection}

\begin{rSubsection}{Big Data Decision Support System}{January 2014 - May 2014}{}{}
\item Acquired business intelligence from USDA dataset using Hadoop with J2EE over the Cloudera interface.
\item Formulated the most feasible manufacturing plant construction cost within each state nationwide.
\item HiveQL along with R extensively used in order to perform the result set for further analysis.
\end{rSubsection}

\begin{rSubsection}{Cost-Benefit Analysis Excel Tool}{January 2014 - May 2014}{}{}
\item Developed a financial tool for valuation of benefits of IT investments considering investment costs.
\item MS Excel application was developed to automate the calculations according to requirements.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%    RESEARCH PAPER SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Paper}

%\begin{rSubsection}{PSP – TSP Software Process}{August 2013 - December 2013}{Purdue University}{West Lafayette, IN}
%\item Analyzed its application and return on investment paralleled to CMMI, Six Sigma and ISO 9001.
%\end{rSubsection}

\begin{rSubsection}{Agile Methodology in Data Quality}{January 2014 - May 2014}{Purdue University}{West Lafayette, IN}
\item Implementing agile methodology in ETL of large scale data.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%    EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
